Supplementary Materials

### 2023-07-11 manuscript/manuscript.tex
ms changes

\begin{abstract}
    Across the human genome, there are large-scale fluctuations in genetic
    diversity caused by the indirect effects of selection. This can be thought
    of as a ``linked selection signal" that reflects selection's effects
    varying according to the placement of functional regions and recombination
    rates along the genome. Previous work has shown that negative selection
    against the steady influx of new deleterious mutations into conserved
    regions is the predominant mode of selection in humans. However, the
    theoretic model that underpins these results, classic Background Selection
    theory, is only applicable when new mutations are so deleterious that they
    cannot drift up in frequency and ultimately fix in the population. Here, we
    develop an alternate theoretic basis for genome-wide linked selection based
    on a quantitative genetics view, which considers the distribution of
    additive fitness variance along the genome. Using a recent model that
    jointly predicts the equilibrium fitness variance and substitution rates
    due to deleterious mutations, we estimate the distribution of selection
    coefficients and mutation rate across three human populations. While our
    model can accommodate weaker selection, we find consistent evidence across
    all populations of very strong selection against deleterious mutations. We
    also find that our model's predicted substitution rates are qualitatively
    consistent with observed divergences in features under weak selective
    constraint like introns and UTRs, but less so in regions under strong
    selective constraint. While our model explains up to 67\% of the out-sample
    variance in diversity at the megabase scale, we find evidence of residual
    strong selection against loss-of-function variants unfit by our model,
    indicating the dominant role negative selection plays in the human genome.
    Altogether, our genome-wide model of the linked selection is a step towards
    uniting evolutionary quantitative genetics with substitution processes.
\end{abstract}

@@

The continual influx of new mutations into populations is the ultimate source
of all adaptations, but the vast majority of mutations either do not affect
fitness or are deleterious. The best predictor of whether a mutation will be
harmful to fitness is if it lands in a functional region, which are often
conserved over deep phylogenetic timescales \parencite{Siepel2005-wh}. Since
such high conservation reflects the product of millions or even billions of
years of evolutionary optimization, it follows that deleterious variants should
be the overwhelming majority of segregating variation in functional regions,
and be responsible for a significant portion of phenotypic variation and
disease \parencite{Zeng2018-ci} (XXX).

Both positive and negative selection stochastically perturb the allele
frequencies of neighboring linked variation in a phenomenon known as linked
selection \parencite{Nordborg1996-nq,Maynard_Smith1974-zr,Barton1998-aj}. While
linked selection processes like sweeps can leave signals on small spatial
scales (XXX), the precise arrangement of functional regions and recombination
rates across the genome leads to a large-scale linked selection signal.

Mutation and negative selection's contribution to this signal is mediated by
the deleterious mutation rate, the strength of selection in conserved segments,
and the spatial distribution of recombination rates and conserved segments.
Since genome-wide recombination maps and putatively conserved segments are
available for many species, researchers have combined these with population
genetic theory to estimate the mutation rate and selection coefficients of
deleterious mutations, as well as the overall reduction in genetic variability
due to the negative selection process.

HERE

As deleterious variation is clustered in functional portions of the genome,
we expect linked selection to reduce levels of diversity surrounding evolutionarily
conserved segments (e.g. genes, regulatory elements, etc.) 
and to shape large-scale spatial patterns in genetic diversity. 
This landscape of diversity is the product of a complex interplay between the
deleterious mutation rate, the local recombination rate, the strength of selection, and
the spatial distribution of conserved segments along a chromosome. 
Since genome-wide recombination maps and putatively conserved segments are available
for many species, there has been consistent effort to fit models of
linked selection to patterns of diversity to estimate population genetic
parameters such as the strength of selection and the deleterious mutation rate 
\parencite{Hudson1995-pt,McVicker2009-ax},
the overall reduction in genetic variability due to the
selection on deleterious variants \parencite{Elyashiv2016-vt,Murphy2022-sj},
and in some cases the rate of beneficial mutations \parencite{corbett2015natural,Elyashiv2016-vt}.

Classic Background Selection (BGS) theory is the predominant theoretic model to
predict the reduction in linked neutral diversity, and is used by statistical
approaches that quantify the aspects of the negative selection. However, the
BGS model makes some assumptions for mathematical tractability that could
distort inferences about the negative selection process. First, since fixation
probabilities ultimately depend on the product of the deleterious selection
coefficient (s) and population size (N), the efficacy of negative selection
should depend on demography. Unfortunately, accommodating demography into
theoretic negative selection models remains an open, difficult problem (XXX).
Second, building off classic models of mutation-selection balance (Crow 1970,
Kimura and Maruyama 196), the Background Selection (XXX) model assumes that new
mutations are sufficiently deleterious that they are invariably driven to loss.
Under this assumption, the effect of selection is well-approximated by simply
rescaling the neutral coalescent by a reduction factor known as B (XXX).
However, this is only appropriate in a limited domain of parameters relevant to
the negative selection process (XXX). Because the BGS model cannot accommodate
the possibility of fixation for mutations with $Ns \ll 1$, diversity is
incorrectly predicted to fall to zero as the strength of selection diminishes.
This weak selection problem is related to the wider problem of modeling the
substitution rate of deleterious mutation (i.e. the “ratchet” rate). Third, the
BGS model assumes segments under purifying selection are sufficiently far apart
that there is no selective interference between them. This is a matter of
degree, since under sufficiently high mutation rates or with little
recombination, selective interference can occur with a segment.

In this work, we extend another class of linked selection models that derive
from quantitative genetics to address limitations of classic background
selection theory. These models suggest that the reduction in pairwise
coalescence times at a position in the genome is determined by the
recombination map and distribution of polygenic additive fitness variance along
the chromosome \parencite{Santiago1998-bs}. This reduction is due to cumulative
effect of stochastic perturbations from selection at other sites. While these
models can theoretically accommodate polygenic fitness variation from any
source as long as its rate of change is not too rapid, we focus specifically on
a deleterious-mutations-only model from Santiago and Caballero (2016). This
model is identical to the classic BGS model when selection against deleterious
mutations is strong, but it also correctly predicts the reduction in diversity
and substitutions rates of weakly deleterious mutations by accurately modeling
levels of genic fitness variation. We extend Santiago and Caballero’s
(hereafter the SC16) model so that it can be used to model genome-wide patterns
of diversity under negative selection processes, and develop Python software to
use this theoretic approach to fit genome-wide models of negative selection.
Using forward simulations, we show this model leads to more accurate DFE
estimates under weak selection. While this new model accommodates the
possibility that a given reduction B could be due to weaker selection, in
applying our composite likelihood method to human population genomic data, we
confirm earlier findings that strong negative selection at a small fraction of
sites fits human data across populations best. Finally, we show that while this
model solves some limitations of the classic BGS model, simulations reveal
another mysterious defect: a poor fit around $Ns=1$. We show that this can be
partially corrected by incorporating the effects of selective interference on
genic variation, but the remaining discrepancy is due to the build up of
negative linkage disequilibrium that cannot be adequately captured by this
model. We find accounting for genic selective interference between segments
fits human population genomic data slightly better, suggesting levels of
negative selection in humans are sufficient to perturb the selection at other
sites.

@@

Our work is motivated by a well-known limitation of classic background
selection theory: it is only accurate for strongly deleterious mutations
\parencite{Charlesworth1993-gb,McVean2000-bt,Good2013-lp,Gordo2002-dr}. Given
statistical methods that fit linked selection processes to genome-wide
diversity data rely on the classic BGS model to estimate the distribution of
fitness effects and rate of deleterious mutations, it is important to
characterize and remedy these shortcomings. However, extending background
selection theory to model weak negative selection is challenging, and it is
worthwhile to develop some intuition for why this is the case, how the classic
background selection works, and how the quantitative genetic model of
\textcite{Santiago2016-mu} solves these problems and can be extended to
genome-wide inference.

Both the classic background selection and SC16 models imagine a negative
selection process where a continual influx of deleterious mutations flow into
the population at a rate of $\mu$ per basepair per generation in a conserved
region of $L$ basepairs, such that the region-wide per generation mutation rate
is $U = \mu L$. Each mutation imposes an additive selective cost of $s$ in
heterozygotes and $2s$ in homozygotes. The classic background selection model
only consider mutations that are sufficiently deleterious that they are
destined to extinction
\parencite{Charlesworth1993-gb,Nordborg1996-nq,Hudson1995-pt,Hudson1994-oh}. In
this case, the genealogy is well-approximated by a neutral coalescence process
with a rescaled effective population size of $N_0 = N \exp(-\nicefrac{U}{s})$.
This approximation works reasonably well for two reasons (though see
\cite{Cvijovic2018-vd,Walczak2012-fi,Nicolaisen2012-vs}). First, when selection
is strong, the number of deleterious mutations per haplotype has a stationary
Poisson distribution with an average equal to the equilibrium under the
deterministic mutation-selection model \parencite{Haldane1927-ga}. Since
lineages carrying strongly deleterious mutations cannot contribute to the
genealogy in the long run, coalescence events only occur in the fraction
$\exp(-\nicefrac{U}{s})$ of the population free of mutations. Second, the time
it takes for a present-day lineage to trace their ancestry back to a
mutation-free ancestor (the ``delay phase") is negligible compared to the
coalescence timescale of $N_0$ among these ancestors (the ``coalescence
phase"), and can be ignored (\cite{Durrett2008-ql}, p. 213;
\cite{Good2014-yz}).

When mutations are only weakly deleterious, their allele frequencies are
strongly influenced by stochastic perturbations and their frequency
trajectories are no longer well-approximated by deterministic models. When
genetic drift is the only source of randomness in allele frequency change, the
relevant scale of stochastic perturbations is determined by the drift-effective
population size $N_e$ (e.g. due to only non-selective process). The insight of
nearly neutral theory \parencite{Ohta1971-gq,Ohta1992-yi} is determined by the
compound parameter $2N_e s$. When $2N_e s \gg 1$, the stochastic component of
allele frequency change is minuscule relative to selection and can be ignored;
this is why the factor that rescales the drift-effective population size under
the BGS model does not depend on $N_e$. However, when $2N_e s \le 1$, the
stochastic perturbations are on a scale equal to or greater than the changes
due to selection. In this regime, weakly deleterious alleles can drift up to
intermediate frequencies before their eventual loss or fixation. When this
occurs, classic BGS theory breaks down for several reasons. First, the ``delay
phase" is no longer negligible as lineages carrying weakly deleterious
mutations can persist on coalescent timescales. This distorts genealogies away
those expected under neutrality
\parencite{Przeworski1999-mb,OFallon2010-my,Higgs1995-xc}. Second, the
distribution of the number of deleterious mutations (and its corresponding
fitness distribution) are no longer stationary and become a traveling wave
\parencite{Rouzine2008-qz,Good2013-lp,Gessler1995-hz} towards reduced
population fitness (since beneficial and back mutations are ignored).
Consequently, individuals in the least-loaded class are stochastically lost,
fixing those mutations with a click of ``Muller's ratchet"
\parencite{Muller1964-ki}. Determining both the rate of Muller's ratchet
\parencite{Haigh1978-gt,Gordo2002-dr,Gessler1995-hz} and the shape of
genealogies under weak selection have been stubborn open problems in
evolutionary genetics.

To further complicate matters, both strong and weakly deleterious mutations
create \emph{heritable} fitness variation. In turn, the presence of heritable
fitness variation generates another source of randomness in allele frequency
change known as genetic \emph{draft} \parencite{Neher2013-dz}. An allele
experiences genetic draft when it becomes randomly associated with a fitness
background, which stochastically perturbs its trajectory across generations.
Like genetic drift, perturbations due to draft are directionless but overall
increase the variance in allele frequency change. Unlike drift, stochastic
perturbations caused by draft are autocorrelated across generations for as long
an allele does not recombine or segregate off its fitness background and the
selective environment does not change
\parencite{Robertson1961-ho,Santiago1995-hx,Buffalo2019-qs}. When selection is
strong, draft can generate multiple-merger coalescences that create
discontinuities in allele frequency trajectories, making diffusion
approximations ill-suited \parencite{Gillespie2000-mh,Der2011-it,Neher2013-dz}.
However, when selection is weak, draft is well-approximated as an increase in
the rate of drift (or equivalently, a reduction in effective population size).

A key insight from Robertson (\citeyear{Robertson1961-ho}) is that in the
long-run weak draft acts like an increase in the variance in offspring number.
\textcite{Wright1938-tv} showed that additional non-heritable variance in
offspring number (e.g. due to mating strategy) rescales the population size
according to,

\begin{align}
    \label{eq:simple_Ne}
    N_e = \frac{2N}{V + 2}
\end{align}
%
where $V$ is the extra variance in offspring number.

However, unlike non-heritable variation in offspring number, the heritable
variation is autocorrelated across generations. At the individual level
Robertson considered, this is because offspring from large families tend to
beget many descendents themselves (and likewise with small families). The same
autocorrelation occurs at the genomic level, as the perturbations to a neutral
allele's trajectory from its particular fitness background tend to occur in the
same direction across generations as long as the linkage exists and the
selective environment is constant. Thus, the total additional heritable
variation in offspring number is the product of the equilibrium additive
fitness variation $V_A$ and an inflation factor $Q_t^2$ due to the build up of
autocorrelation to generation $t$. We let $Q^2 := Q_t^2$ as $t \to \infty$.
Intuitively, the product $V_A Q^2$ represents the expected total variance in
reproductive success a neutral mutation experiences over its lifetime in a
system with weak selection draft. Incorporating the impact of time-invariant
autocorrelation created by draft as a rescaled rate of drift is analogous to
using the Green--Kubo relation to find the transport coefficient in molecular
dynamics with velocity autocorrelation \parencite{Green1954-kl,Kubo1957-va}.

Including the total asymptotic variance in reproductive success in Equation
\eqref{eq:simple_Ne} and assuming Wright--Fisher levels of non-heritable
variation (i.e. $V = 2 + 4 Q^2 V_A$), the draft-effective population size $N_d$
is

\begin{align}
    \label{eq:main_Ne}
    N_d = \frac{N}{Q^2 V_A + 1}
\end{align}

(c.f. \cite{Robertson1961-ho,Santiago1995-hx}; see Supplementary Section
\ref{supp:theory} for a proof). In general, however, statistics such as
heterozygosity depend on the cumulative autocorrelation factor up to some time
$t$, $Q_t^2$ \parencite[p. 2111]{Santiago1998-bs}. This reflects the fact that
effective population size experienced by a mutation newly associated with a
fitness background is larger than the asymptotic effective population size,
since not much autocorrelation has accumulated in the stochastic perturbations
caused by drift yet. From a backwards-time perspective, this reflects the fact
that pairwise diversity (which is approximately heterozygosity when $2N\mu \ll
1$) depends on the pairwise coalescence rate per generation, which is not
constant under draft. The benefit of using Robertson's forward-time model of
draft is that the inflation factor is invariant with respect to the particular
fitness background the neutral allele becomes stochastically associated with.
By contrast, the difficulty with modeling draft backwards in time is that the
coalescence rates experienced by a lineage are not invariant to which lineage
was sampled due to its particular associated fitness background.

@@

While using Equation \eqref{eq:Va} in Equation \eqref{eq:main_Ne} leads to a
prediction for the draft-effective population size $N_d$, closed-form
expressions for the rate of the ratchet $R$ have generally been hard to find
\parencite{Haigh1978-gt,Higgs1995-xc,Gessler1995-hz}. The key insight of
\textcite{Santiago2016-mu} is that the ratchet rate under draft is determined
by the probability of fixation $p_F(N_d, s)$
\parencite{Kimura1962-su,Malecot1948-zv} using the draft-rescaled effective
population size, i.e. $R = N U p_F(N_d, s)$. Given this equation for the
ratchet and Equation \eqref{eq:polygenic_Ne} for $N_d$ under draft, we have a
system of two non-linear equations that can be solved numerically for $N_d$ and
$R$ for each segment,

>>>>

\begin{abstract}

    Across the human genome, there are large-scale fluctuations in genetic
    diversity caused by the indirect effects of selection. This can be thought
    of as a ``linked selection signal" that reflects selection's effects
    varying according to the placement of functional regions and recombination
    rates along the genome. Previous work has shown that negative selection
    against the steady influx of new deleterious mutations into conserved
    regions is the predominant mode of selection in humans. However, the
    theoretic model that underpins these results, classic Background Selection
    theory, is only applicable when new mutations are so deleterious that they
    cannot drift up in frequency and ultimately fix in the population. Here, we
    develop an alternate theoretic basis for genome-wide linked selection based
    on a quantitative genetics view, which considers how diversity is reduced
    according to the arrangement of additive fitness variance along the genome.
    Using a recent model that jointly predicts the equilibrium fitness variance
    and substitution rates due to deleterious mutations, we estimate the
    distribution of selection coefficients and mutation rate across three human
    populations. While our model can accommodate weaker selection, we find
    consistent evidence across all populations of very strong selection against
    deleterious mutations. We also find that our model's predicted substitution
    rates are qualitatively consistent with observed divergences in features
    under weak selective constraint like introns and UTRs, but less so in
    regions under strong selective constraint. While our model explains up to
    67\% of the out-sample variance in diversity at the megabase scale, we find
    evidence of residual strong selection against loss-of-function variants
    unfit by our model, indicating the dominant role negative selection plays
    in the human genome. Altogether, our genome-wide model of the linked
    selection is a step towards uniting evolutionary quantitative genetics with
    substitution processes.

\end{abstract}

@@

The continual influx of new mutations into populations is the ultimate source
of all adaptations, but the vast majority of mutations either do not affect
fitness or are deleterious. Negative selection (i.e. purifying selection) works
to eliminate these deleterious mutations from the population, thus we expect
them to appear at low frequencies within populations
\parencite{Haldane1927-ga}, and less likely to fix between lineages. The best
predictor of whether a new mutation will reduce fitness is if it occurs in a
functional region of the genome, which are often conserved over deep
phylogenetic timescales \parencite{Siepel2005-wh,Margulies2003-sn}. Since these
conserved regions reflect the product of millions of years of evolutionary
optimization, it follows that deleterious variants should be the overwhelming
majority of segregating variation in these regions. Furthermore, rare variation
in these regions is responsible for a significant portion of phenotypic
variation and disease in humans
\parencite{Zeng2018-ci,Lek2016-cb,Karczewski2020-ky,Tennessen2012-ge}.

Selection on both beneficial and deleterious variants perturbs the allele
frequencies of neighboring linked sites, a phenomenon known as linked selection
\parencite{Nordborg1996-nq,Maynard_Smith1974-zr,Barton1998-aj,Charlesworth1993-gb}.
Since deleterious variation is clustered in functional portions of the genome,
we expect linked selection to reduce levels of diversity around conserved
segments (e.g. genes, regulatory elements, etc.). The genomic arrangement of
these evolutionarily conserved regions and recombination rates create a
large-scale spatial signal of the linked selection process in genetic diversity
along the genome. Since genome-wide recombination maps and putatively conserved
segments are available for many species, there has been consistent effort to
fit models to this linked selection signal to estimate population genetic
parameters such as the strength of selection and the deleterious mutation rate
\parencite{Hudson1995-pt,McVicker2009-ax}, as well as distinguish and quantify
the roles of positive and negative selection and estimate the rate of
beneficial mutations \parencite{Elyashiv2016-vt,Murphy2022-sj}. In humans,
previous work has shown that negative selection plays the dominant role in
shaping megabase-scale patterns of diversity, with positive selection playing a
nearly negligible role \parencite{Murphy2022-sj}.

Prior work to model the reduction in linked diversity due to deleterious
mutations has largely relied on the classic Background Selection (BGS) model
\parencite{Charlesworth1993-gb,Nordborg1996-nq,Hudson1995-pt,Hudson1995-xc}.
While this model has been successful in explaining many patterns of diversity,
some its simplifying assumptions may distort inferences about the negative
selection process. First, since fixation probabilities ultimately depend on the
product of the deleterious selection coefficient (s) and population size (N),
the efficacy of negative selection should depend on demography. Unfortunately,
accommodating demography into theoretic negative selection models remains an
open, difficult problem \parencite{Zeng2013-ep,Johri2020-oj}. Second, building
off classic models of mutation-selection balance
\parencite{Crow1970-wm,Kimura1966-bk}, the BGS model assumes that new mutations
are sufficiently deleterious that they are invariably driven to loss. Under
this assumption, the effect of selection is well-approximated by simply
rescaling the neutral coalescent by a reduction factor known as $B =
\nicefrac{N}{N_e}$ \parencite{Charlesworth2013-kl}. However, this simple
rescaling approach is not appropriate across parts of parameter space that are
relevant to natural populations \parencite{McVean2000-bt,Good2014-yz}. In
particular, the BGS model cannot accommodate the possibility of fixation for
mutations with $Ns \ll 1$, diversity is incorrectly predicted to fall to zero
as the strength of selection diminishes. This weak selection problem is related
to the wider problem of modeling the substitution rate of deleterious mutation
(i.e. the “ratchet” rate) and incorporating the impact of perturbations from
selective interference.

In this work, we extend another class of linked selection models that derive
from quantitative genetics to address limitations of the classic BGS model.
These models express linked selection in terms of how polygenic fitness
variance creates weak genetic draft, and which increases pairwise coalescence
rates. While these models can theoretically accommodate additive fitness
variance from any source as long as its rate of change is not too rapid, we
focus specifically on a deleterious-mutations-only model of fitness variance
from \textcite{Santiago2016-mu}. This model is identical to BGS when selection
against deleterious mutations is strong, but it also correctly predicts the
reduction in diversity when selection is weak by jointly predicting the
deleterious substitution rate. We extend the Santiago and Caballero (hereafter
the SC16) model of the negative selection process so that it can be fit to
patterns of genome-wide diversity, according to the spatial distribution of
genomic features that could harbor deleterious fitness variation. Using forward
simulations, we show this model leads to more accurate estimates of the
distribution of fitness effects under weak selection. Finally, we apply our
composite-likelihood method to human population genomic data and provide new
estimates of the negative selection process in humans.

@@

Similar to previous work, we aim to characterize the negative selection process
through the signal left on nucleotide diversity at linked sites. Although
nucleotide diversity is a less-informative statistic than the full site
frequency spectrum, it is much easier to derive theoretic models of how
selection alters expected pairwise coalescence times at linked sites than to
describe the entire genealogy. Still, inferences drawn from the linked
selection signal about selective processes are only as accurate as the
underlying theoretic model. Our work is motivated by a well-known limitation of
classic background selection theory: it only accurately predicts levels of
linked diversity when new mutations are strongly deleterious
\parencite{Charlesworth1993-gb,McVean2000-bt,Good2013-lp,Gordo2002-dr}.
However, developing linked selection theory that accommodates weak selection
has been challenging problem \parencite{Good2014-yz,Haigh1978-gt,Higgs1995-xc},
and it is worthwhile to develop in intuition for how the classic BGS model
works, and how quantitative genetic models of linked selection can alleviate
these problems and be extended to genome-wide inference.

Both the classic background selection and SC16 models imagine a negative
selection process where a continual influx of deleterious mutations flow into
the population at a rate of $\mu$ per basepair per generation in a conserved
region of $L$ basepairs, such that the region-wide per generation mutation rate
is $U = \mu L$. Each mutation imposes an additive selective cost of $s$ in
heterozygotes and $2s$ in homozygotes. The classic background selection model
only considers mutations that are sufficiently deleterious that they are
destined to extinction
\parencite{Charlesworth1993-gb,Nordborg1996-nq,Hudson1995-pt,Hudson1994-oh}. In
this case, the genealogy is well-approximated by a neutral coalescence process
with a rescaled effective population size of $N_0 = N \exp(-\nicefrac{U}{s})$.
This approximation works reasonably well for two reasons (though see
\cite{Cvijovic2018-vd,Walczak2012-fi,Nicolaisen2012-vs}). First, when selection
is strong, the number of deleterious mutations per haplotype has a stationary
Poisson distribution with an average equal to the equilibrium under the
deterministic mutation-selection model \parencite{Haldane1927-ga}. Since
lineages carrying strongly deleterious mutations cannot contribute to the
genealogy in the long run, coalescence events only occur in the fraction
$\exp(-\nicefrac{U}{s})$ of the population free of mutations. Second, the time
it takes for a present-day lineage to trace their ancestry back to a
mutation-free ancestor (the ``delay phase") is negligible compared to the
coalescence timescale of $N_0$ among these ancestors (the ``coalescence
phase"), and can be ignored (\cite{Durrett2008-ql}, p. 213;
\cite{Good2014-yz}).

By contrast, the frequency trajectories of weakly deleterious mutations are
strongly impacted by stochastic perturbations, so deterministic models no
longer provide a good approximation. When genetic drift is the only source of
these randomness in allele frequency change, the relevant scale of stochastic
perturbations is determined by the drift-effective population size $N_e$
\parencite{Ohta1971-gq,Ohta1992-yi}. Under weak selection ($2N_e s \le 1$), the
stochastic perturbations are on a scale equal to or greater than the changes
due to selection. Then, weakly deleterious alleles can by chance drift up to
intermediate frequencies before their eventual loss or fixation. Classic BGS
breaks down in this domain, since the ``delay phase" is no longer negligible
and genealogies are no longer well-approximated by a neutral coalescence
process \parencite{Przeworski1999-mb,OFallon2010-my,Higgs1995-xc}. Moreover,
the distribution of the number of deleterious mutations (and its corresponding
fitness distribution) are no longer stationary and become a traveling wave
\parencite{Rouzine2008-qz,Good2013-lp,Gessler1995-hz} towards reduced
population fitness (since beneficial and back mutations are ignored). When this
occurs, individuals in the least-loaded class are stochastically lost, fixing
those mutations with a click of ``Muller's ratchet" \parencite{Muller1964-ki}.
Determining both the rate of Muller's ratchet
\parencite{Haigh1978-gt,Gordo2002-dr,Gessler1995-hz} and the shape of
genealogies under weak selection have been stubborn open problems in
evolutionary genetics.

To further complicate matters, when selection is weak, the stochastic
perturbations from selection at neighboring sites generates another source of
randomness in allele frequency change known as genetic \emph{draft}
\parencite{Neher2013-dz}. An allele experiences genetic draft when it becomes
randomly associated with a fitness background, which stochastically perturbs
its trajectory across generations. Like genetic drift, perturbations due to
draft are directionless but overall increase the variance in allele frequency
change. Unlike drift, stochastic perturbations caused by draft are
autocorrelated across generations for as long an allele does not recombine or
segregate off its fitness background and the selective environment does not
change \parencite{Robertson1961-ho,Santiago1995-hx,Buffalo2019-qs}. When
selection is strong, draft can generate multiple-merger coalescences that
create discontinuities in allele frequency trajectories, making diffusion
approximations ill-suited \parencite{Gillespie2000-mh,Der2011-it,Neher2013-dz}.
However, when selection is weak, draft is well-approximated as an increase in
the rate of drift (or equivalently, a reduction in effective population size).

Quantitative genetics models of linked selection formulate the impact of weak
draft in terms of additive genetic fitness variance, which can more readily
accommodate weak selection. This idea derives from a key insight from Robertson
(\citeyear{Robertson1961-ho}): in the long-run, the effect of weak draft on
neutral allele frequencies acts like an increase in the variance in offspring
number. However, unlike non-heritable variation in offspring number, the
heritable variation that generates draft is autocorrelated across generations.
At the individual level Robertson considered, this is because offspring from
large families tend to beget many descendents themselves (and likewise with
small families). The same autocorrelation occurs at the genomic level, as the
perturbations to a neutral allele's trajectory from its particular fitness
background tend to occur in the same direction across generations as long as
the linkage exists and the selective environment is constant. Thus, the total
additional heritable variation in offspring number is the product of the
equilibrium additive fitness variation $V_A$ in a generation and an inflation
factor $Q_t^2$ due to the build up of autocorrelation to generation $t$. We let
$Q^2 := Q_t^2$ as $t \to \infty$. Intuitively, the product $V_A Q^2$ represents
the expected total variance in reproductive success a neutral mutation
experiences over its lifetime in a system with weak selection draft.

We can include this total additional variance into expressions for effective
population size as we would larger variance in family sizes due to
non-heritable causes \parencite{Wright1938-tv}. We define the draft-effective
population size $N_d$ as

\begin{align}
    \label{eq:main_Ne}
    N_d = \frac{N}{Q^2 V_A + 1}
\end{align}
%
(c.f. \cite{Robertson1961-ho,Santiago1995-hx}; see Supplementary Section
\ref{supp:theory} for a proof). The benefit of modeling draft with Robertson's
forward-time model is that the inflation factor is invariant with respect to
the particular fitness background the neutral allele becomes stochastically
associated with. By contrast, the difficulty with modeling draft backwards in
time is that the coalescence rates experienced by a lineage are not invariant
to which lineage was sampled due to its particular associated fitness
background.

@@

While using Equation \eqref{eq:Va} in Equation \eqref{eq:main_Ne} leads to a
prediction for the draft-effective population size $N_d$, closed-form
expressions for the rate of the ratchet $R$ have generally been hard to find
\parencite{Haigh1978-gt,Higgs1995-xc,Gessler1995-hz}. The key insight of
\textcite{Santiago2016-mu} is that the ratchet rate under draft is determined
by the probability of fixation $p_F(N_d, s)$
\parencite{Kimura1962-su,Malecot1952-qh} using the draft-rescaled effective
population size, i.e. $R = N U p_F(N_d, s)$. Given this equation for the
ratchet and Equation \eqref{eq:polygenic_Ne} for $N_d$ under draft, we have a
system of two non-linear equations that can be solved numerically for $N_d$ and
$R$ for each segment,

### 2023-07-11 manuscript/supplementary.tex
ms changes

\begin{align}
  \E(S_1 S_2) &= \E(S_1^2) (1-\kappa)(1-r) = \E(S_1^2) Q_2^2 \nonumber \\
  \E(S_1 S_3) &= \E(S_1^2) (1-\kappa)^2(1-r)^2 = \E(S_1^2) Q_3^2.
\end{align}
%
The $Q_t^2$ terms represent the inflation of variance due to autocovariance in
frequency change across generations due to weak draft.

@@

Under Santiago and Caballero's model, the correct effective population size to
gauge reduction in heterozygosity or coalescent times is given by their
equation 4 \parencite{Santiago2016-mu}. This equation considers how the
inflation factor $Q_t^2$ that sets the draft-effective population size varies
over $t$. This is because selective processes can lead to non-constant pairwise
coalescent rates, which impact pairwise coalescent rates and thus the reduction
factor. We experimented with calculating this full sum and integral
approximations to it in our methods, but it seemed to make little difference in
our application. Additionally, it was too costly to calculate computationally
for genome-wide calculations of the B' map. Instead, we solve for the
asymptotic $\widetilde{N}_{e,\infty}$ for each segment, and use that to
calculate the log reduction factor under the SC16 model, $b'$.

>>>>

\begin{align}
  \E(S_1 S_2) &= \E(S_1^2) (1-\kappa)(1-r) = \E(S_1^2) Q_2^2 \nonumber \\
  \E(S_1 S_3) &= \E(S_1^2) (1-\kappa)^2(1-r)^2 = \E(S_1^2) Q_3^2.
\end{align}
%
The $Q_t^2$ terms represent the inflation of variance due to autocovariance in
frequency change across generations due to weak draft. Incorporating the impact
of time-invariant autocorrelation created by draft as a rescaled rate of drift
is analogous to using the Green--Kubo relation to find the transport
coefficient in molecular dynamics with velocity autocorrelation
\parencite{Green1954-kl,Kubo1957-va}.

@@

Under Santiago and Caballero's model, the correct effective population size to
gauge reduction in heterozygosity or coalescent times is given by their
equation 4 \parencite{Santiago2016-mu}. This equation considers how the
inflation factor $Q_t^2$ that sets the draft-effective population size varies
over $t$. This is because statistics such as heterozygosity depend on the
cumulative autocorrelation factor up to some time $t$, $Q_t^2$ \parencite[p.
2111]{Santiago1998-bs}. This reflects the fact that effective population size
experienced by a mutation newly associated with a fitness background is larger
than the asymptotic effective population size, since not much autocorrelation
has accumulated in the stochastic perturbations caused by drift yet. From a
backwards-time perspective, this reflects the fact that pairwise diversity
(which is approximately heterozygosity when $2N\mu \ll 1$) depends on the
pairwise coalescence rate per generation, which is not constant under draft.

We experimented with calculating this full sum and integral approximations to
it in our methods, but it seemed to make little difference in our application.
Additionally, it was too costly to calculate computationally for genome-wide
calculations of the B' map. Instead, we solve for the asymptotic
$\widetilde{N}_{e,\infty}$ for each segment, and use that to calculate the log
reduction factor under the SC16 model, $b'$.
